\section{Common Uses}

The TalkBox device is designed for users with a verbal impairment. The profiles loaded onto the TalkBox Device can be selected or adjusted based on user needs. Some common scenarios in which users may find the TalkBox device most useful are as follows. These common use scenarios are audio profiles and buttons that are pre-loaded onto the TalkBox device. 

\begin{enumerate}
\end{enumerate}
\begin{enumerate}
\item General purpose education: Yes, No, I understand, I don't understand, Can you explain more?, I would like assistance
\item Emotions: Happy, Sad, Excited, Confused, Anxious, Bored
\item Weather: Sunny, Rainy, Cloudy, Snowy, Icy, Hot, Warm, Chilly, Cold, Freezing, Windy
\item Hospital: Yes, No, I am in pain, I am okay, Help!
\item Restaurant: Menu, Water, Restroom, I would like to order something, Thank you, May I have the bill?
\end{enumerate}
\medskip

The TalkBox device is designed to be fully configurable based on user needs. Functions such as number of buttons or profiles on the TalkBox device can be determined by the user. It is recommended that these functions are determined based on consideration of the environment in which is it meant to be used. 
\newline 

For example, the "Hospital" profile listed above is limited to five  buttons, as a pressing situation such as a hospital visit may require a simple interface of only essential buttons. In comparison, profiles such as "Weather", most commonly used for daily journal-keeping or educational activities, can be more extensive in its descriptive level. 

